### 2015-05-14 background.tex
fix
improvements in bg

The most common technique for eliminating races is using a lock $l$. Locking a set of program statements that access a shared resource with $l$ creates a \emph{critical section}, i.e.\ source code that can only execute by the thread that holds $l$. Figure~\ref{fig:lock_example} shows how to use a lock to eliminate the data race in Figure~\ref{fig:data_race_example}. The example is tricky, because the return statement can potentially race on the \texttt{f\_pos} field. To fix this issue, we store the result in a temporary variable, inside the critical section.

Lock-based synchronization is a powerful tool for preventing data races in drivers, but careless use of locks has multiple pitfalls~\cite{sutter2005software}. Coarse-grained locking can hurt performance, because it limits the opportunity for concurrency. On the other hand, fine-grained locking can easily lead to deadlocks. Although the Linux kernel provides sophisticated lock-free synchronization mechanisms~\cite{corbet2005linux}, such as atomic read and write operations, in this work we focus on locks. However, we still treat lock-free operations (e.g.\ atomics) soundly (see Definition~\ref{definition:datarace}), by not regarding them as providing any protection between threads. This is sound but can potentially introduce false positives.

>>>>

The most common technique for eliminating races is using a lock $l$. Locking a set of program statements that access a shared resource with $l$ creates a \emph{critical section}, i.e.\ source code that can only execute by the thread that holds $l$. Figure~\ref{fig:lock_example} shows how to use a lock to eliminate the races in Figure~\ref{fig:data_race_example}. The example is tricky, because the return statement can potentially race on the \texttt{f\_pos} field. To fix this issue, we store the result in a temporary variable, inside the critical section.

Lock-based synchronization is a powerful tool for preventing races in drivers, but careless use of locks has many pitfalls~\cite{sutter2005software}. Coarse-grained locking can hurt performance, as it limits the opportunity for concurrency. On the other hand, fine-grained locking can easily lead to deadlocks. Although the Linux kernel provides sophisticated lock-free synchronization mechanisms~\cite{corbet2005linux}, such as atomic read and write operations, in this work we focus on locks. However, we still treat lock-free operations soundly (see Definition~\ref{definition:datarace}), by not regarding them as providing any protection between threads. This is sound, but can potentially introduce false positives.
